SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-06 docs/questioning.tex
minor change

In this section we categorize and describe the various mechanisms
developed to detect the attacks described in
Section~\ref{sec:attacks}. We accompany our descriptions
with comments related to the following dimensions:
a) diagnostic performance, b) security, c) ease of use
and d) detection locus. Regarding the other two
dimensions we provide general remarks in our upcoming
``Analysis" section (\ref{sec:analysis}).

>>>>

In this section we categorize and describe the various mechanisms
developed to detect the attacks described in
Section~\ref{sec:attacks}. We accompany our descriptions
with comments related to the following dimensions:
a) diagnostic performance, b) computational performance,
c) security, d) ease of use, and e) detection locus.
Regarding the availability dimension we provide a general
comment in our upcoming ``Analysis" section (\ref{sec:analysis}).
